```{r}
library(MASS)
library(ISLR2)
rm(list=ls())
```



13a-c) the length of y is 100, β_0 = -1, β_1 = .5
```{r}
set.seed(1)
x = rnorm(100)
eps = rnorm(100,sd=.25)
y = -1+.5*x+eps
length(y)
```
d) The plot shows a positive linear relationship between x and y
```{r}
plot(x,y)
```

e) The predicted coefficients are close to equal to the true coefficients.
```{r}
model = lm(y~ x)
summary(model)

```

f)
```{r}
plot(x,y)
abline(model)
legend("topright", legend = c("Positive Trend Line"))
```

g) There is no evidence to suggest adding x^2 will improve the model fit.
```{r}
model2 = lm(y~x + I(x^2))
summary(model2)
```

h) points are a lot closer to the line
```{r}
set.seed(1)
x = rnorm(100)
eps = rnorm(100,sd=.1)
y = -1+.5*x+eps
model2 = lm(y~x)
plot(x,y)
abline(model2)
```
i) points are further from the line
```{r}
set.seed(1)
x = rnorm(100)
eps = rnorm(100,sd=.5)
y = -1+.5*x+eps
model3 = lm(y~x)
plot(x,y)
abline(model3)
```
j) confidence interval gets wider with more variance on the error term
```{r}
confint(model)
confint(model2)
confint(model3)
```

